High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data\vspace*{\fill}

### 2015-11-22 rmarkdown/prelims_paper.Rnw
Added section on strand cc

\[
\mbox{NSC} = \frac{ \max }{\min}
\]

>>>>

\[
\mbox{NSC} = \frac{ \max_\delta y(\delta)}{\min_\delta y(\delta)}
\]

where $y(\delta)$ is strand cross-correlation defined as in (\ref{scc}).

\subsubsection{Strand cross-correlation}
\label{sec:scc}

The strand cross-correlation (SCC) was proposed by Kharchenko et al.,
2008 \cite{strandcc} and it may be one of the most used of the
ChIP-Seq QC metrics. The SCC curve is defined as:

\begin{align}
  y(\delta) = \sum_c w_c r\left[ n_c^+ \left(x + \frac{\delta}{2}
    \right), n_c^- \left( x- \frac{\delta}{2} \right)\right]
\label{scc}
\end{align}

where $y(\delta)$ is strand cross-correlation for a strand shift
$\delta$, $r$ is the Pearson correlation, $w_c$ is the propotion of
tags mapped to chromosome $c$ and $n_c^S$ is the tag count vector for
strand $S$ and chromsome $c$.
